---
title: "<center>ReadMe</center>"
author: "<center>Oeng Sopheap</center>"
date: "<center>06/09/2022</center>"
output:
  rmarkdown::html_document:
    theme: cerulean
    #code_folding: hide
---

```{r setup, message=TRUE, warning=TRUE, include=FALSE, paged.print=TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

## 1. Introduction

Generate accurately and comprehensively microbiology report are time consuming and intensive effort needed. Unfortunately, microbiology report is crucial and useful for microbiologists, laboratory manager, clinicians, hospital management and other relevant stakeholders for quality improvement.

To assist microbiologists in Cambodia who are using [CamLIS](www.camlis.net), we ([DMDP](www.dmdp.org) and microbiologists from laboratories) developed R script and Rmarkdown to clean, analyse and automate report in a timely manner.

## 2. Objectives

This document is developed to guide microbiologists to understand and able to generate Microbiology Report in R programming.

## 3. Requirements  

R is a free programming language and support for Window, Mac and Linux operating system.

  
Installing R programming and code editor:

a\. Install R commander: [www.r-project.org](https://cran.r-project.org)

b\. Install R Studio (code editor): [R studio free desktop](https://www.rstudio.com/products/rstudio/download/).

c\. Install R packages: open R studio

```{r, eval=FALSE}
install.packages("tidyverse")
install.packages("here")
install.packages("janitor")
install.packages("kableExtra")
install.packages("AMR")
install.packages("readxl")
install.packages("plotly")
```

Note: install R programming and packages only apply for first time.

## 4. Microbiology Report folder 2022

a\. Files:

-   *Microbiology Report.Rprof*- project file
-   *Run.R*- run this file to generate report
-   *Readme.html*- instruction for running R programming
-   *Microbiology_Report\_'Date'.html*- report
-   Dictionary \*Dictionary.xlsx\*- choose hospital to analyse, start date, end date, number of the top rows to skip and person/team generate report.

b\. Folder:
-   image- store image files in *.png*
-   code- store files *.Rmd* and *.R*
-   outputs- output files (*Microbiology_Report\_'Date'.html*)
-   data:
    -   Excel file extracted from CamLIS *Bacteriology Report.xlsx*
    -   Dictionary *Dictionary.xlsx*

## 5. R script and Rmarkdown

R script and Rmarkdown are published in [www.github.com/sopheap15](www.github.com/sopheap15) for easily update and accessible for all users. Folder *data* and *outputs* are excluded in Github to avoid leaking data. Users requires to add these two folders after download.

Users can download the whole folder from Github with click on code button and then find download option. Alternative option, users can clone by using commend *git clone https://github.com/Sopheap15/Microbiology-report.git.*

## 6. Analysis

-   Adjust in dictionary for hospital, date to analyse, For end date, the default is 31-12-202_. It will automatic analyse based on the last date of column collection date in data.
-   Drop your data from CamLIS *Bacteriology Report.xlsx* in folder *data*
-   Double click on \*Microbiology Report\_'Date'.Rprof
-   Open Run.R
-   Click on Run or Shortcut "Command/Ctr + A + Enter"
-   Output folder: open *Microbiology_Report\_'Date'.html* with google chrome or other up to date web browsers

## 7. Contact

Contact DMDP laboratory mentors for any questions or contact by email: [oeng.sopheap\@dmdp.org](mailto:oeng.sopheap@dmdp.org), tel: 012 40 63 88


